Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Add section in related work related to merging duplicate bug reports

%TODO: ADD HERE PROPER PAPER
However, the study conducted by Cavalcanti et. al \cite{cavalcanti2013bug} shows completely 
different results. The authors investigated around 280,000 tickets from multiple open and 
closed source repositories and found that having bug duplicates
97,000 tickets from the Mozilla repository in order to infer the quality of merging duplicate
bug reports. Their results are statistically significant and they show that merging bug report 
duplicates improved the overall quality of the project (i.e. )

@@

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

One other improvement to the application could be adding more robust support for statistical analysis. At the moment, 
our tool uses our own custom types and functions for generating Welch T Test and Spearman R Test results, and even if 
it produces the expected \emph{p} and \emph{r coefficient} values, end users of the application might want to 
analyse even more possible correlations. As the Go community lacks native libraries to perform statistical tests, 
the users of our tool might miss the simplicity of running such tests in R. A solution can be to integrate the 
Roger library \cite{r_stats} inside the stats package, which basically allows any Go application to communicate with 
R via TCP.

>>>>

Another study that investigates duplicate bug reports is the work conducted by Prifti et. al \cite{prifti2011detecting}. 
The authors first collected 75,000 bug reports from Bugzilla for the Firefox project. Then, they created a tool 
for detecting bug report duplicates with an accuracy of 53\%. However, due to prior 
findings showing both that duplicate reports can improve the quality \cite{bettenburg2008duplicate}
but also decrease it \cite{cavalcanti2013bug}, this study tries to achieve a middle ground - 
before the reporter can file the bug in the system, the duplicate detection tool previously 
described runs and checks whether there are any duplicates. If there are, the user is presented 
with the possibility of simply adding extra information, if suitable, to one of the duplicates 
found. This is indeed a novel approach that can bring great benefits to the software engineering 
community and the authors state that they wish to pursue future work on this idea.

@@

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

One other improvement to the application could be adding more robust support for statistical analysis. At the moment, 
our tool uses our own custom types and functions for generating Welch T Test and Spearman R Test results, and even if 
it produces the expected \emph{p} and \emph{r coefficient} values, end users of the application might want to 
analyse even more possible correlations. As the Go community lacks native libraries to perform statistical tests, 
the users of our tool might miss the simplicity of running such tests in R. A solution can be to integrate Senseye's 
Roger library \cite{r_stats} inside the stats package, which basically allows any Go application to communicate with 
R via TCP.
